Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
minor changes
Interval arithmetic reference

There are two approaches for the {\sc verify} phase based on the
described model.  The first uses interval arithmetic 
\cdsay{Dario, can you please add a reference here?} to represent the
coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
and the rounding operations outwards during the process. 
%\cdsay{dario, what coefficients are these?}
% This results in a
% tighter calculation of the error at the cost of
% performance.
Synthesised controllers using this verifier will always
be correct and only generate counterexamples when the precision of the
engine is insuficient.  Given the high computational cost of this
approach, we also designed a second approach, which we describe below.
Our experimental results described in Sec.~\ref{sec:experiments},  
%try both approaches and provide the time for the fastest. 
show that the increase in speed of the second approach 
over the first one is in most cases of several orders of magnitude.

@@

All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440 with 96\,GB
of RAM, and Linux OS.  All times given are wall clock time in seconds as measured
by the UNIX date command.  For the inductive back-end we apply a timeout of 8 hours
per benchmark, and 24 hours for the interval arithmetic back-end.

>>>>

There are two approaches for the {\sc verify} phase based on the
described model.  The first uses interval arithmetic \cite{moore1966interval}
to represent the coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
and rounds operations outwards during calculations. 
%\cdsay{dario, what coefficients are these?}
% This results in a
% tighter calculation of the error at the cost of
% performance.
Synthesised controllers using this verifier will always
be correct and only generate counterexamples when the precision of the
engine is insuficient.  Given the high computational cost of this
approach, we also designed a second approach, which we describe below.
Our experimental results described in Sec.~\ref{sec:experiments},  
%try both approaches and provide the time for the fastest. 
show that the increase in speed of the second approach 
over the first one is in most cases of several orders of magnitude.

@@

All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440 with 96\,GB
of RAM, and Linux OS.  All times given are wall clock time in seconds as measured
by the UNIX date command.  For the inductive back-end, we apply a timeout of 8 hours
per benchmark, and 24 hours for the interval arithmetic back-end.
